### 2013-12-17 poster_new/conference_poster_4.tex
new design for poster - format

\begin{poster}
{
headerborder=closed, % Adds a border around the header of content boxes
colspacing=1em, % Column spacing
%bgColorOne=white, % Background color for the gradient on the left side of the poster
bgColorOne=col1,
%bgColorTwo=white, % Background color for the gradient on the right side of the poster
bgColorTwo=col2,
borderColor=lightblue, % Border color
headerColorOne=black, % Background color for the header in the content boxes (left side)
headerColorTwo=lightblue, % Background color for the header in the content boxes (right side)
headerFontColor=white, % Text color for the header text in the content boxes
boxColorOne=white, % Background color of the content boxes
textborder=roundedleft, % Format of the border around content boxes, can be: none, bars, coils, triangles, rectangle, rounded, roundedsmall, roundedright or faded
eyecatcher=true, % Set to false for ignoring the left logo in the title and move the title left
headerheight=0.1\textheight, % Height of the header
headershape=roundedright, % Specify the rounded corner in the content box headers, can be: rectangle, small-rounded, roundedright, roundedleft or rounded
headerfont=\Large\bf\textsc, % Large, bold and sans serif font in the headers of content boxes
%textfont={\setlength{\parindent}{1.5em}}, % Uncomment for paragraph indentation
linewidth=2pt % Width of the border lines around content boxes
}
%----------------------------------------------------------------------------------------
%	TITLE SECTION 
%----------------------------------------------------------------------------------------
%
{\includegraphics[height=4em]{logo.png}} % First university/lab logo on the left
{\bf\textsc{Hierarchical Controller Architecture in Software Defined Networks}\vspace{0.5em}} % Poster title
{\textsc{\{ Gourav Khaneja, Sweta Seethamraju \& Praveen Kumar \} \hspace{12pt}}} % Author names and institution
{\includegraphics[height=4em]{logo.png}} % Second university/lab logo on the right

>>>>

\begin{poster}
{
headerborder=closed, % Adds a border around the header of content boxes
colspacing=1em, % Column spacing
%bgColorOne=white, % Background color for the gradient on the left side of the poster
bgColorOne=col1,
%bgColorTwo=white, % Background color for the gradient on the right side of the poster
bgColorTwo=col2,
borderColor=lightblue, % Border color
headerColorOne=black, % Background color for the header in the content boxes (left side)
headerColorTwo=lightblue, % Background color for the header in the content boxes (right side)
headerFontColor=white, % Text color for the header text in the content boxes
boxColorOne=white, % Background color of the content boxes
textborder=roundedleft, % Format of the border around content boxes, can be: none, bars, coils, triangles, rectangle, rounded, roundedsmall, roundedright or faded
eyecatcher=false, % Set to false for ignoring the left logo in the title and move the title left
headerheight=0.1\textheight, % Height of the header
headershape=roundedright, % Specify the rounded corner in the content box headers, can be: rectangle, small-rounded, roundedright, roundedleft or rounded
headerfont=\Large\bf\textsc, % Large, bold and sans serif font in the headers of content boxes
%textfont={\setlength{\parindent}{1.5em}}, % Uncomment for paragraph indentation
linewidth=2pt % Width of the border lines around content boxes
}
%----------------------------------------------------------------------------------------
%	TITLE SECTION 
%----------------------------------------------------------------------------------------
%
{\includegraphics[height=4em]{logo.png}} % First university/lab logo on the left
{\bf\textsc{Hierarchical Controller Architecture in Software Defined Networks}\vspace{0.5em}} % Poster title
{\textsc{\{ Gourav Khaneja, Sweta Seethamraju \& Praveen Kumar \} \hspace{12pt}}} % Author names and institution
{\hspace{120pt} \includegraphics[height=8em]{UIUC_logo.png}} % Second university/lab logo on the right
